Usage metrics

### 2020-12-16 analysis/usage.Rmd

>>>>

```{r exercised-call-site-per-variant}
static_eval <- P %>% filter(call_fun_name == "eval") %>% nrow()
static_evalq <- P %>% filter(call_fun_name == "evalq") %>% nrow()
static_eval.parent <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
static_local <- P %>% filter(call_fun_name == "local") %>% nrow()

overview_table(
  r("StaticEval", static_eval),
  r("StaticEvalq", static_evalq),
  r("StaticEvalParent", static_eval.parent),
  r("StaticLocal", static_local),
  r("TriggeredEval", trig_eval),
  r("TriggeredEvalq", trig_evalq),
  r("Triggeredevalparent", trig_eval.parent),
  r("Triggeredlocal", trig_local),
  r("Triggeredevalpercent", ratio(trig_eval, static_eval)),
  r("Triggeredevalqpercent", ratio(trig_evalq, static_evalq)),
  r("Triggeredevalparentpercent", ratio(trig_eval.parent, static_eval.parent)),
  r("Triggeredlocalpercent", ratio(trig_local, static_local))
) -> TBL
```
